\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-10-11 paper/main.tex
moved methods after intro, finished draft of results section up to (before) exploratory analyses

\newcommand{\frDetail}{S1}
\newcommand{\natDetail}{S2}
\newcommand{\vocabDetail}{S3}
\newcommand{\spatialDetail}{S4}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/behavior_overview_immediate}
\caption{\textbf{Immediate memory tests.}}
\label{fig:immediate_behavior}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/behavior_overview_delayed}
\caption{\textbf{Delayed memory tests.}}
\label{fig:delayed_behavior}
\end{figure}

\begin{itemize}
\item characterizing behaviors (color by quartile and continue the
  color scheme in later figures-- hue reflects task, shading reflects
  performance.  white outline means immediate, black outline means delayed)
  \begin{itemize}
  \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
    recall performance).  
    Figure~\ref{fig:fr_behavioral}.
    \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
      movie/recall trajectories (color: mean precision).  Figure~\ref{fig:nat_behavioral}.
    \item Foreign language flashcards (immediate + delayed):
      p(correct) histogram (color: p(correct)).  Figure~\ref{fig:vocab_behavioral}.
      \item Spatial learning: mean error by number of shapes (color:
        intercept and slope of line fit to errors as a function of the number of
        shapes).  Figure~\ref{fig:spatial_behavioral}.
      \end{itemize}
    \item Fitness info (break down by task performance, potentially
      separately for each task); also separate out recent (raw) and
      recent versus baseline -- color using same color scheme as
      behavior figure
      \begin{itemize}
      \item activity (steps, zone minutes, floors/elevation)
      \item resting heart rate
        \item sleep
        \end{itemize}
  \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
          tasks.  Diagonal: histogram of performance metric for that
          task.  Above-diagonal entries: compare performance across
          tasks (by subject).  Below-diagonal entries: empty?
          density/2d histograms?
    \begin{itemize}
    \item Memory-memory
    \item fitness-fitness
    \item survey-survey
    \item (fitness + survey)-memory
    \end{itemize}
  \item predictive analysis (regressions)
    \begin{itemize}
    \item Predict memory performance on held-out task from other tasks
    \item Predict memory performance on each task using fitness data
      \item Predict memory performance on each task using survey data
      \end{itemize}
    \item Reverse correlations: look at recent changes versus baseline
      trends (color using same scheme as behavior figures).  Possibly 
      \begin{itemize}
      \item Fitness profile that predicts performance on each task (barplots + timelines)
      \item Fitness profile for each survey demographic (barplots + timelines)
        \begin{itemize}
          \item Select out mental health demographics (based on meds, stress levels)
          \end{itemize}
        \end{itemize}
  \end{itemize}

@@

The fitness tracking data associated with participants' Fitbit
accounts varied in scope and duration according to which device the
participant owned (Fig.~\ref{fig:devices}), how often the participant
wore (and/or synced) their tracking device, and how long they had
owned their device.  For example, while all participants' devices
supported basic activity metrics such as daily step counts, only a
subset of the devices with heart rate monitoring capabilities provided
information about workout intensity, resting heart rate, and other
related measures.

\begin{figure}[t]
\centering
\includegraphics[width=0.6\textwidth]{figs/devices}
\caption{\textbf{Fitbit devices.}  The bars indicate the numbers of
  participants whose fitness tracking data came from each model of
  Fitbit device.  ``MobileTrack'' refers to participants who used
  smartphone accelerometer information to track their activity via the
  Fitbit smartphone app.
  ``Unknown''  denotes participants whose device information was not
  available from their available Fitbit data.}
\label{fig:devices}
\end{figure}

@@

>>>>

\newcommand{\devices}{S1}
\newcommand{\frDetail}{S2}
\newcommand{\natDetail}{S3}
\newcommand{\vocabDetail}{S4}
\newcommand{\spatialDetail}{S5}
\newcommand{\fitDists}{S6}
\newcommand{\fitDistgridImmediate}{S7}
\newcommand{\fitScatterImmediate}{S8}
\newcommand{\fitDistgridDelayed}{S9}
\newcommand{\fitScatterDelayed}{S10}

@@

@@

The fitness tracking data associated with participants' Fitbit
accounts varied in scope and duration according to which device the
participant owned (Fig.~\devices), how often the participant
wore (and/or synced) their tracking device, and how long they had
owned their device.  For example, while all participants' devices
supported basic activity metrics such as daily step counts, only a
subset of the devices with heart rate monitoring capabilities provided
information about workout intensity, resting heart rate, and other
related measures.

@@

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/behavior_overview_immediate}
\caption{\textbf{Immediate memory tests.}  \textbf{a. Free recall.}
  Left: probability of recalling each word first as a function of its
  presentation position.  Middle: probability of transitioning between
successively recalling the word presented at position $i$, followed by
word presented at position $i + \mathrm{Lag}$.  Right: probability of
recalling each word as a function of its presentation position.  See
Figure~\frDetail~for additional details.
\textbf{b. Naturalistic recall.}  Top: 2D embedding of a 2.5~min video
clip; each dot reflects a narrative event (red denotes early events
and blue denotes later events).  Bottom: 2D embedding of the averaged
transcripts of participants' recountings of the narrative (dots: same
format as top panel).  The arrows denote the average trajectory
directions through the corresponding region of text embedding space,
for any participants whose recountings passed through that region.
Blue arrows denote statistically reliable agreement across
participants ($p < 0.05$, corrected).  See Figure~\natDetail~for
additional details.  \textbf{c. Foreign language
  flashcards.} Each bar denotes the average proportion of correctly
recalled Gaelic-English word pairs from early (first 3), late (last
3), or all (i.e., all 10) study positions.  See
Figure~\vocabDetail~for additional details.\textbf{d. Spatial
  learning.}  Average estimation error in shape locations as a
function of the number of shapes.  See Figure~\spatialDetail~for
additional details.  All panels: error bars and error
ribbons denote bootstrap-estimated 95\% confidence intervals.  Shading
(saturation) denotes results for different subsets of participants
assigned based on their task performance (Figs.~\frDetail,
\natDetail, \vocabDetail, and \spatialDetail~provide information about
which performance metrics and values the shading reflects; in general
more saturated colors denote participants who performed better on the
given task.)  In Panel d, participants are grouped in two ways; in the
left panel, participants are grouped according to the $y$-intercepts of regression lines (estimation error as a
function of the number of shapes); in the right panel, participants
are grouped according to the slopes of the same regression lines.}
\label{fig:immediate_behavior}
\end{figure}

\begin{figure}[tp]
\centering
\includegraphics[width=1\textwidth]{figs/behavior_overview_delayed}
\caption{\textbf{Delayed memory tests.}  \textbf{a.  Free recall.}
  These panels are in the same format as
  Figure~\ref{fig:immediate_behavior}a, but they reflect performance
  on the delayed free recall task.  For additional details see
  Figure~\frDetail.  \textbf{b. Naturalistic recall.}  These panels
  are in the same format as Figure~\ref{fig:immediate_behavior}b, but
  the right panel reflects performance on the delayed naturalistic
  recall task.  For additional details see Figure~\natDetail.
  \textbf{c. Foreign language flashcards.} This panel is in the same
  format as Figure~\ref{fig:immediate_behavior}c, but it reflects
  performance on the delayed flashcards test.  For additional details
  see Figure~\vocabDetail.}
\label{fig:delayed_behavior}
\end{figure}

In addition to observing substantial across-participant variability in
memory performance, we also observed substantial variability in
participants' fitness and activity metrics
(Fig.~\ref{fig:fitness_summary}).  We examined recent measurements,
averaged over the week prior to testing
(Fig.~\ref{fig:fitness_summary}a), baselined measurements (average
over the prior week, divided by the average over the preceding 30 day;
Fig.~\ref{fig:fitness_summary}b), along with more gradually varying
measures that tended to remain relatively static over timescales of
weeks to months (Fig.~\ref{fig:fitness_summary}c).
Figure~\fitDists~displays across-participant
distributions for a broad selection of these measures, and Figures~\fitDistgridImmediate,
\fitScatterImmediate, \fitDistgridDelayed, and \fitScatterDelayed~show
different participants' fitness metrics, broken down by their
performance on different memory tasks.

\begin{figure}[tp]
\centering
\includegraphics[width=0.8\textwidth]{figs/fitness_distributions_summary}
\caption{\textbf{Fitness measures.}  \textbf{a. Recent measures.}
  Resting heart rate (HR) and daily step counts, averaged over the
  week prior to testing.  \textbf{Baseline-normalized measures.}
  Resting heart rate and daily step counts averaged over the week
  prior to testing, divided by the average resting heart rate and step
counts averaged over the preceding month.  \textbf{Static measures.}
Body mass index (BMI), body fat percentage, and weight (in kg).  For
more information see Figures~\fitDists, \fitDistgridImmediate,
\fitScatterImmediate, \fitDistgridDelayed, and \fitScatterDelayed.}
\label{fig:fitness_summary}
\end{figure}

\begin{itemize}
% \item characterizing behaviors (color by quartile and continue the
%   color scheme in later figures-- hue reflects task, shading reflects
%   performance.  white outline means immediate, black outline means delayed)
%   \begin{itemize}
%   \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
%     recall performance).  
%     Figure~\ref{fig:fr_behavioral}.
%     \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
%       movie/recall trajectories (color: mean precision).  Figure~\ref{fig:nat_behavioral}.
%     \item Foreign language flashcards (immediate + delayed):
%       p(correct) histogram (color: p(correct)).  Figure~\ref{fig:vocab_behavioral}.
%       \item Spatial learning: mean error by number of shapes (color:
%         intercept and slope of line fit to errors as a function of the number of
%         shapes).  Figure~\ref{fig:spatial_behavioral}.
%       \end{itemize}
%     \item Fitness info (break down by task performance, potentially
%       separately for each task); also separate out recent (raw) and
%       recent versus baseline -- color using same color scheme as
%       behavior figure
%       \begin{itemize}
%       \item activity (steps, zone minutes, floors/elevation)
%       \item resting heart rate
%         \item sleep
%         \end{itemize}
  \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
          tasks.  Diagonal: histogram of performance metric for that
          task.  Above-diagonal entries: compare performance across
          tasks (by subject).  Below-diagonal entries: empty?
          density/2d histograms?
    \begin{itemize}
    \item Memory-memory
    \item fitness-fitness
    \item survey-survey
    \item (fitness + survey)-memory
    \end{itemize}
  \item predictive analysis (regressions)
    \begin{itemize}
    \item Predict memory performance on held-out task from other tasks
    \item Predict memory performance on each task using fitness data
      \item Predict memory performance on each task using survey data
      \end{itemize}
    \item Reverse correlations: look at recent changes versus baseline
      trends (color using same scheme as behavior figures).  Possibly 
      \begin{itemize}
      \item Fitness profile that predicts performance on each task (barplots + timelines)
      \item Fitness profile for each survey demographic (barplots + timelines)
        \begin{itemize}
          \item Select out mental health demographics (based on meds, stress levels)
          \end{itemize}
        \end{itemize}
  \end{itemize}

### 2021-10-11 paper/supplement.tex
writing up behavioral results [WIP]
moved methods after intro, finished draft of results section up to (before) exploratory analyses

\title{\textit{Supplementary materials for} Fitness tracking reveals task-specific associations between
  memory, mental health, and exercise}
\author[1, $\star$]{Jeremy R. Manning}
\author[1,2]{Gina M. Notaro}
\author[1]{Esme Chen}
\author[1]{Paxton C. Fitzpatrick}
\affil[1]{Dartmouth College, Hanover, NH}
\affil[2]{Lockheed Martin, Bethesda, MD}
\affil[$\star$]{Address correspondence to jeremy.r.manning@dartmouth.edu}

@@

@@

>>>>

\title{\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between
  memory, mental health, and exercise}
\author[1, $\star$]{Jeremy R. Manning}
\author[1,2]{Gina M. Notaro}
\author[1]{Esme Chen}
\author[1]{Paxton C. Fitzpatrick}
\affil[1]{Dartmouth College, Hanover, NH}
\affil[2]{Lockheed Martin, Bethesda, MD}
\affil[$\star$]{Address correspondence to jeremy.r.manning@dartmouth.edu}

@@

\renewcommand{\thefigure}{S\arabic{figure}}

\begin{figure}[p]
\centering
\includegraphics[width=0.6\textwidth]{figs/devices}
\caption{\textbf{Fitbit devices.}  The bars indicate the numbers of
  participants whose fitness tracking data came from each model of
  Fitbit device.  ``MobileTrack'' refers to participants who used
  smartphone accelerometer information to track their activity via the
  Fitbit smartphone app.
  ``Unknown''  denotes participants whose device information was not
  available from their available Fitbit data.}
\label{fig:devices}
\end{figure}

@@

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_distributions}
\caption{\textbf{Distributions of fitness measures.}}
\label{fig:fitness_dists}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_dists_immediate}
\caption{\textbf{Distributions of fitness measures, broken down
    by immediate task performance.}}
\label{fig:fitness_dists_immediate}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_scatter_immediate}
\caption{\textbf{Scatterplots of fitness measures versus
    immediate task performance measures.}}
\label{fig:fitness_scatters_immediate}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_dists_delayed}
\caption{\textbf{Distributions of fitness measures, broken down
    by delayed task performance.}}
\label{fig:fitness_dists_delayed}
\end{figure}

\begin{figure}[p]
\centering
\includegraphics[width=\textwidth]{figs/fitness_scatter_delayed}
\caption{\textbf{Scatterplots of fitness measures versus
    delayed task performance measures.}}
\label{fig:fitness_scatters_delayed}
\end{figure}
